Linking hypothesis and number of response options modulate inferred scalar implicature rate

### 2018-05-10 writeup.Rmd
formulae rendered as equations in gd
some styling changes

  - name          : "Masoud Jasbi"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "XXX Postal address"
    email         : "XXX my@email.com"
  - name          : "Brandon Waldon"
    affiliation   : "1"
  - name          : "Judith Degen"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Stanford University"
author_note: |
  XXX Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  The past 15 years have seen increasing experimental investigations of core pragmatic questions in the ever more active and lively field of experimental pragmatics. Within experimental pragmatics, many of the core questions have relied on the operationalization of the theoretical notion of 'implicature rate'. Implicature rate based results have informed the work on acquisition, online processing, and scalar diversity, inter alia. Despite its theoretical importance. Implicature rate has  typically been quantified as the proportion of 'pragmatic' judgments in two-alternative forced choice truth value judgment tasks. Despite its theoretical importance, this linking hypothesis from implicature rate to behavioral responses has never been extensively tested. Here we show that two factors dramatically affect the 'implicature rate' inferred from truth value judgment tasks: a) the number of responses provided to participants; and b) the linking hypothesis about what constitutes a 'pragmatic' judgment. We argue that it is time for the field of experimental pragmatics to engage more seriously with its foundational assumptions about how theoretical notions map onto behaviorally measurable quantities, and present a sketch of an alternative linking hypothesis that derives behavior in truth value judgment tasks from probabilistic utterance expectations.
keywords          : "scalar implicature; methodology; linking hypothesis; experimental pragmatics; truth value judgment task"
wordcount         : "X"
bibliography      : ["r-references.bib"]
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no
class             : "man"
output            : papaja::apa6_pdf
editor_options: 
  chunk_output_type: inline
---

@@

```{r speakerprobs, message=FALSE, warning=FALSE,fig.cap = "Speaker probabilities of utterances on the exhaustive and scalar trials, as obtained using the model described in this section."}

@@

speaker_probs %>%
  ggplot(aes(x=u, y=prob)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
  facet_wrap(~s) +
  labs(x="", y= paste("Speaker probability ", "S(u | s)"))+
  # theme_few() +
  theme(text = element_text(size=12), axis.text.x = element_text(angle = 45, hjust = 1))
  scale_fill_manual(values = c("red4", "springgreen3"), guide=FALSE)
```

>>>>

  - name          : "Masoud Jasbi"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Margaret Jacks Hall, Building 460 Rm. 127, Stanford, CA, 94305-2150"
    email         : "masoudj@stanford.edu"
  - name          : "Brandon Waldon"
    affiliation   : "1"
  - name          : "Judith Degen"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Stanford University, Department of Linguistics"
author_note: |
  XXX Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  The past 15 years have seen increasing experimental investigations of core pragmatic questions in the ever more active and lively field of experimental pragmatics. Within experimental pragmatics, many of the core questions have relied on the operationalization of the theoretical notion of 'implicature rate'. Implicature rate based results have informed the work on acquisition, online processing, and scalar diversity, inter alia. Despite its theoretical importance. Implicature rate has  typically been quantified as the proportion of 'pragmatic' judgments in two-alternative forced choice truth value judgment tasks. Despite its theoretical importance, this linking hypothesis from implicature rate to behavioral responses has never been extensively tested. Here we show that two factors dramatically affect the 'implicature rate' inferred from truth value judgment tasks: a) the number of responses provided to participants; and b) the linking hypothesis about what constitutes a 'pragmatic' judgment. We argue that it is time for the field of experimental pragmatics to engage more seriously with its foundational assumptions about how theoretical notions map onto behaviorally measurable quantities, and present a sketch of an alternative linking hypothesis that derives behavior in truth value judgment tasks from probabilistic utterance expectations.
keywords          : "scalar implicature; methodology; linking hypothesis; experimental pragmatics; truth value judgment task"
wordcount         : "X"
bibliography      : ["r-references.bib"]
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no
class             : "man"
output            : papaja::apa6_pdf
editor_options: 
  chunk_output_type: inline
---

@@

```{r speakerprobs, message=FALSE, warning=FALSE, fig.cap = "Speaker probabilities of utterances on the exhaustive and scalar trials, as obtained using the model described in this section."}

@@

speaker_probs %>%
  ggplot(aes(x=u, y=prob)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
  facet_wrap(~s) +
  labs(x="", y= paste("Speaker probability ", "S(u | s)"))+
  # theme_few() +
  theme(text = element_text(size=12), axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = c("red4", "springgreen3"), guide=FALSE)
```

### 2018-05-10 writeup.tex
some styling changes

The study was administered online through Amazon Mechanical
Turk.\footnote{The experiment can be viewed
  \href{https://cdn.rawgit.com/thegricean/si-paradigms/94a590f0/experiments/main/1_methods/online_experiment/connective_game.html}{here}.}
Participants were first introduced to the set of cards we used in the
study (Figure \ref{fig:stimuli}). Each card depicted one or two animals,
where an animal could be either a cat, a dog, or an elephant. Then
participants were introduced to a blindfolded fictional character called
Bob. Bob was blindfolded to avoid violations of ignorance expectations
associated with the use of disjunction ({\textbf{???}}; Chierchia et
al., 2001) Participants were told that Bob would guess the contents of
the cards and their task was to indicate whether Bob's guess was wrong
or right. On each trial, participants saw a card and a sentence
representing Bob's guess. For example, they saw a card with a cat and
read the sentence \enquote{There is a cat on the card.} They then
provided an assessment of Bob's guess. The study ended after 24 trials.

@@

\begin{verbatim}
## <ggproto object: Class ScaleDiscrete, Scale>
##     aesthetics: fill
##     axis_order: function
##     break_info: function
##     break_positions: function
##     breaks: waiver
##     call: call
##     clone: function
##     dimension: function
##     drop: TRUE
##     expand: waiver
##     get_breaks: function
##     get_breaks_minor: function
##     get_labels: function
##     get_limits: function
##     guide: FALSE
##     is_discrete: function
##     is_empty: function
##     labels: waiver
##     limits: NULL
##     make_sec_title: function
##     make_title: function
##     map: function
##     map_df: function
##     n.breaks.cache: NULL
##     na.translate: TRUE
##     na.value: NA
##     name: waiver
##     palette: function
##     palette.cache: NULL
##     position: left
##     range: <ggproto object: Class RangeDiscrete, Range>
##         range: NULL
##         reset: function
##         train: function
##         super:  <ggproto object: Class RangeDiscrete, Range>
##     reset: function
##     scale_name: manual
##     train: function
##     train_df: function
##     transform: function
##     transform_df: function
##     super:  <ggproto object: Class ScaleDiscrete, Scale>
\end{verbatim}

@@

\hypertarget{ref-BenzGotzner2014}{}
Benz, A., \& Gotzner, N. (2014). Embedded implicatures revisited: Issues
with the Truth-Value Judgment Paradigm. In J. Degen, M. Franke, \& N. D.
Goodman (Eds.), \emph{Proceedings of the formal \& experimental
pragmatics workshop, european summer school for language, logic and
information (esslli)} (pp. 1--6). Tübingen.

@@

\hypertarget{ref-burkner2016brms}{}
Bürkner, P.-C., \& others. (2016). Brms: An r package for bayesian
multilevel models using stan. \emph{Journal of Statistical Software},
\emph{80}(1), 1--28.

\hypertarget{ref-Chemla2011}{}
Chemla, E., \& Spector, B. (2011). Experimental Evidence for Embedded
Scalar Implicatures. \emph{Journal of Semantics}, \emph{28}(3),
359--400.

\hypertarget{ref-chierchia2001}{}
Chierchia, G., Crain, S., Teresa, M., Guasti, M. T., Gualmini, A., \&
Meroni, L. (2001). The Acquisition of Disjunction: Evidence for a
Grammatical View of Scalar Implicatures. In A. H.-J. D. Et al. (Ed.),
\emph{BUCLD 25 proceedings} (pp. 157--168). Somerville, MA: Cascadilla
Press.

\hypertarget{ref-DeNeys2007}{}
De Neys, W., \& Schaeken, W. (2007). When People Are More Logical Under
Cognitive Load - Dual Task Impact on Scalar Implicature.
\emph{Experimental Psychology}, \emph{54}(2), 128--133.
doi:\href{https://doi.org/10.1027/1618-3169.54.2.128}{10.1027/1618-3169.54.2.128}

\hypertarget{ref-Degen2015}{}
Degen, J. (2015). Investigating the distribution of 'some' (but not
'all') implicatures using corpora and web-based methods. \emph{Semantics
and Pragmatics}, \emph{8}(11), 1--55.
doi:\href{https://doi.org/10.3765/sp.8.11}{10.3765/sp.8.11}

\hypertarget{ref-Degen2014}{}
Degen, J., \& Goodman, N. D. (2014). Lost your marbles? The puzzle of
dependent measures in experimental pragmatics. \emph{Proceedings of the
36th Annual Conference of the Cognitive Science Society}, 397--402.

@@

\hypertarget{ref-DegenTanenhaus2016}{}
Degen, J., \& Tanenhaus, M. K. (2016). Availability of Alternatives and
the Processing of Scalar Implicatures: A Visual World Eye-Tracking
Study. \emph{Cognitive Science}, \emph{40}(1), 172--201.
doi:\href{https://doi.org/10.1111/cogs.12227}{10.1111/cogs.12227}

\hypertarget{ref-Degen2013}{}
Degen, J., Franke, M., \& Jäger, G. (2013). Cost-Based Pragmatic
Inference about Referential Expressions. \emph{Proceedings of the 35th
Annual Conference of the Cognitive Science Society (CogSci'13)},
376--281.

@@

\hypertarget{ref-Franke2016}{}
Franke, M., \& Jäger, G. (2016). Probabilistic pragmatics, or why Bayes
' rule is probably important for pragmatics. \emph{Zeitschrift Für
Sprachwissenschaft}, \emph{35}(1), 3--44.

@@

\hypertarget{ref-Goodman2016}{}
Goodman, N. D., \& Frank, M. C. (2016). Pragmatic Language
Interpretation as Probabilistic Inference. \emph{Trends in Cognitive
Sciences}, \emph{20}(11), 818--829.
doi:\href{https://doi.org/10.1016/j.tics.2016.08.005}{10.1016/j.tics.2016.08.005}

@@

\hypertarget{ref-grice1975}{}
Grice, H. P. (1975). Logic and Conversation. \emph{Syntax and
Semantics}, \emph{3}, 41--58. Retrieved from
\href{http://books.google.com/books?hl=en\%7B/\&\%7Dlr=\%7B/\&\%7Did=hQCzOmaGeVYC\%7B/\&\%7Doi=fnd\%7B/\&\%7Dpg=PA121\%7B/\&\%7Ddq=Logic+and+conversation\%7B/\&\%7Dots=j7aijUymwm\%7B/\&\%7Dsig=iV1rz1eEm4ns6bQ6CevIURXFVO4}{http://books.google.com/books?hl=en\{\textbackslash{}\&\}lr=\{\textbackslash{}\&\}id=hQCzOmaGeVYC\{\textbackslash{}\&\}oi=fnd\{\textbackslash{}\&\}pg=PA121\{\textbackslash{}\&\}dq=Logic+and+conversation\{\textbackslash{}\&\}ots=j7aijUymwm\{\textbackslash{}\&\}sig=iV1rz1eEm4ns6bQ6CevIURXFVO4}

@@

\hypertarget{ref-Horowitz2017}{}
Horowitz, A. C., Schneider, R. M., \& Frank, M. C. (2017). The Trouble
With Quantifiers: Exploring Children's Deficits in Scalar Implicature.
\emph{Child Development}, 1--40.
doi:\href{https://doi.org/10.1111/cdev.13014}{10.1111/cdev.13014}

@@

\hypertarget{ref-Noveck2001}{}
Noveck, I. (2001). When children are more logical than adults:
experimental investigations of scalar implicature. \emph{Cognition},
\emph{78}(2), 165--188. Retrieved from
\url{http://www.ncbi.nlm.nih.gov/pubmed/11074249}

@@

\hypertarget{ref-Noveck2003}{}
Noveck, I., \& Posada, A. (2003). Characterizing the Time Course of an
Implicature: an Evoked Potentials Study. \emph{Brain and Language},
\emph{85}(2), 203--210.
doi:\href{https://doi.org/10.1016/S0093-934X(03)00053-1}{10.1016/S0093-934X(03)00053-1}

\hypertarget{ref-Papafragou2004}{}
Papafragou, A., \& Tantalou, N. (2004). Children's Computation of
Implicatures. \emph{Language Acquisition}, \emph{12}(1), 71--82.

@@

\hypertarget{ref-Qing2015}{}
Qing, C., \& Franke, M. (2015). Variations on a bayesian theme:
Comparing bayesian models of referential reasoning. In H. Zeevat \&
H.-C. Schmitz (Eds.), \emph{Bayesian natural language semantics and
pragmatics} (Vol. 2, pp. 201--220). Cham, Switzerland: Springer
International Publishing.
doi:\href{https://doi.org/10.1007/978-3-319-17064-0_9}{10.1007/978-3-319-17064-0\_9}

@@

\hypertarget{ref-Stiller2015}{}
Stiller, A. J., Goodman, N. D., \& Frank, M. C. (2015). Ad-hoc
Implicature in Preschool Children. \emph{Language Learning and
Development}, \emph{11}(2), 176--190.
doi:\href{https://doi.org/10.1080/15475441.2014.927328}{10.1080/15475441.2014.927328}

>>>>

The study was administered online through Amazon Mechanical
Turk.\footnote{The experiment can be viewed
  \href{https://cdn.rawgit.com/thegricean/si-paradigms/94a590f0/experiments/main/1_methods/online_experiment/connective_game.html}{here}.}
Participants were first introduced to the set of cards we used in the
study (Figure \ref{fig:stimuli}). Each card depicted one or two animals,
where an animal could be either a cat, a dog, or an elephant. Then
participants were introduced to a blindfolded fictional character called
Bob. Bob was blindfolded to avoid violations of ignorance expectations
associated with the use of disjunction (Chierchia et al., 2001;
Sauerland, 2004) Participants were told that Bob would guess the
contents of the cards and their task was to indicate whether Bob's guess
was wrong or right. On each trial, participants saw a card and a
sentence representing Bob's guess. For example, they saw a card with a
cat and read the sentence \enquote{There is a cat on the card.} They
then provided an assessment of Bob's guess. The study ended after 24
trials.

@@

@@

\hypertarget{ref-BenzGotzner2014}{}
Benz, A., \& Gotzner, N. (2014). Embedded implicatures revisited: Issues
with the Truth-Value Judgment Paradigm. In J. Degen, M. Franke, \& N. D.
Goodman (Eds.), \emph{Proceedings of the formal \& experimental
pragmatics workshop, European Summer School for Language, Logic and
Information (ESSLLI)} (pp. 1--6). Tübingen.

@@

\hypertarget{ref-burkner2016brms}{}
Bürkner, P.-C., \& others. (2016). brms: An R package for bayesian
multilevel models using Stan. \emph{Journal of Statistical Software},
\emph{80}(1), 1--28.

\hypertarget{ref-Chemla2011}{}
Chemla, E., \& Spector, B. (2011). Experimental evidence for embedded
scalar implicatures. \emph{Journal of Semantics}, \emph{28}(3),
359--400.

\hypertarget{ref-chierchia2001}{}
Chierchia, G., Crain, S., Teresa, M., Guasti, M. T., Gualmini, A., \&
Meroni, L. (2001). The acquisition of disjunction: Evidence for a
grammatical view of scalar implicatures. In Anna H.-J. Do Laura
Domínguez \& A. Johansen (Eds.), \emph{Proceedings of the 25th annual
boston university conference on language development} (pp. 157--168).
Somerville, MA: Cascadilla Press.

\hypertarget{ref-DeNeys2007}{}
De Neys, W., \& Schaeken, W. (2007). When people are more logical under
cognitive load - dual task impact on scalar implicature.
\emph{Experimental Psychology}, \emph{54}(2), 128--133.
doi:\href{https://doi.org/10.1027/1618-3169.54.2.128}{10.1027/1618-3169.54.2.128}

\hypertarget{ref-Degen2015}{}
Degen, J. (2015). Investigating the distribution of ``some'' (but not
``all'') implicatures using corpora and web-based methods.
\emph{Semantics and Pragmatics}, \emph{8}(11), 1--55.
doi:\href{https://doi.org/10.3765/sp.8.11}{10.3765/sp.8.11}

\hypertarget{ref-Degen2014}{}
Degen, J., \& Goodman, N. D. (2014). Lost your marbles? The puzzle of
dependent measures in experimental pragmatics. In P. Bello, M. Guarini,
M. McShane, \& B. Scassellati (Eds.), \emph{Proceedings of the 36th
annual conference of the cognitive science society} (pp. 397--402).

@@

\hypertarget{ref-DegenTanenhaus2016}{}
Degen, J., \& Tanenhaus, M. K. (2016). Availability of alternatives and
the processing of scalar implicatures: A visual world eye-tracking
study. \emph{Cognitive Science}, \emph{40}(1), 172--201.
doi:\href{https://doi.org/10.1111/cogs.12227}{10.1111/cogs.12227}

\hypertarget{ref-Degen2013}{}
Degen, J., Franke, M., \& Jäger, G. (2013). Cost-based pragmatic
inference about referential expressions. \emph{Proceedings of the 35th
Annual Conference of the Cognitive Science Society}, 376--281.

@@

\hypertarget{ref-Franke2016}{}
Franke, M., \& Jäger, G. (2016). Probabilistic pragmatics, or why Bayes'
rule is probably important for pragmatics. \emph{Zeitschrift Für
Sprachwissenschaft}, \emph{35}(1), 3--44.

@@

\hypertarget{ref-Goodman2016}{}
Goodman, N. D., \& Frank, M. C. (2016). Pragmatic language
interpretation as probabilistic inference. \emph{Trends in Cognitive
Sciences}, \emph{20}(11), 818--829.
doi:\href{https://doi.org/10.1016/j.tics.2016.08.005}{10.1016/j.tics.2016.08.005}

@@

\hypertarget{ref-grice1975}{}
Grice, H. P. (1975). Logic and conversation. \emph{Syntax and
Semantics}, \emph{3}, 41--58.

@@

\hypertarget{ref-Horowitz2017}{}
Horowitz, A. C., Schneider, R. M., \& Frank, M. C. (2017). The trouble
with quantifiers: Exploring children's deficits in scalar implicature.
\emph{Child Development}, 1--40.
doi:\href{https://doi.org/10.1111/cdev.13014}{10.1111/cdev.13014}

@@

\hypertarget{ref-Noveck2001}{}
Noveck, I. (2001). When children are more logical than adults:
experimental investigations of scalar implicature. \emph{Cognition},
\emph{78}(2), 165--188.

@@

\hypertarget{ref-Noveck2003}{}
Noveck, I., \& Posada, A. (2003). Characterizing the time course of an
implicature: An evoked potentials study. \emph{Brain and Language},
\emph{85}(2), 203--210.
doi:\href{https://doi.org/10.1016/S0093-934X(03)00053-1}{10.1016/S0093-934X(03)00053-1}

\hypertarget{ref-Papafragou2004}{}
Papafragou, A., \& Tantalou, N. (2004). Children's computation of
implicatures. \emph{Language Acquisition}, \emph{12}(1), 71--82.

@@

\hypertarget{ref-Qing2015}{}
Qing, C., \& Franke, M. (2015). Variations on a Bayesian theme:
Comparing Bayesian models of referential reasoning. In H. Zeevat \&
H.-C. Schmitz (Eds.), \emph{Bayesian natural language semantics and
pragmatics} (Vol. 2, pp. 201--220). Cham, Switzerland: Springer
International Publishing.
doi:\href{https://doi.org/10.1007/978-3-319-17064-0_9}{10.1007/978-3-319-17064-0\_9}

\hypertarget{ref-sauerland2004scalar}{}
Sauerland, U. (2004). Scalar implicatures in complex sentences.
\emph{Linguistics and Philosophy}, \emph{27}(3), 367--391.

@@

\hypertarget{ref-Stiller2015}{}
Stiller, A. J., Goodman, N. D., \& Frank, M. C. (2015). Ad-hoc
implicature in preschool children. \emph{Language Learning and
Development}, \emph{11}(2), 176--190.
doi:\href{https://doi.org/10.1080/15475441.2014.927328}{10.1080/15475441.2014.927328}
